Procurements of the Canadian Government, Runaway Military Contracts

### 2024-11-30 paper/paper.qmd
updated appendix A

# Step 6: Create the ggplot2 bar chart
ggplot(contract_counts_df, aes(x = amount_label, y = Contract_Count_k)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  scale_y_continuous(
    labels = if (max_count >= 1000) {
      label_number(scale = 1, accuracy = 1)
    } else {
      label_number(accuracy = 1)
    },
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(
    title = "Number of Contracts per 10,000 CAD Award Amount Range",
    x = "Award Amount (Thousands)",
    y = paste0("Number of Contracts ", if (max_count >= 1000) "(Thousands)" else ""),
    caption = "Data includes contracts <= 100,000 CAD."
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.caption = element_text(hjust = 0.5, size = 10, face = "italic")
  )

@@

4. The for-loop simply runs "click download -> click next page" process 329 times, however IJF may add more pages so modify total_pages to scrape the number of pages IJF is offering. In the event of an error mid-way through scraping take note of which page failed to download (page that you are on is printed to the console) and simply set the start of the for-loop. After restarting the loop be sure to verify that the next downloaded page is the correct one, otherwise you will have to restart the process from step 1.

@@

>>>>

# Step 6: Create the ggplot2 bar chart
ggplot(contract_counts_df, aes(x = amount_label, y = Contract_Count_k)) +
  geom_bar(stat = "identity", fill = "skyblue", color = "black") +
  scale_y_continuous(
    labels = if (max_count >= 1000) {
      label_number(scale = 1, accuracy = 1)
    } else {
      label_number(accuracy = 1)
    },
    expand = expansion(mult = c(0, 0.05))
  ) +
  labs(
    title = "Number of Contracts per 10,000 CAD Award Amount Range",
    x = "Award Amount (Thousands)",
    y = paste0("Number of Contracts ", if (max_count >= 1000) "(Thousands)" else ""),
    caption = "Data includes contracts <= 100,000 CAD."
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 10),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    plot.caption = element_text(hjust = 0.5, size = 10, face = "italic")
  )
```

@@

4. The for-loop simply runs "click download -> click next page" process 329 times, however IJF may add more pages so modify total_pages to scrape the number of pages IJF is offering. In the event of an error mid-way through scraping take note of which page failed to download (page that you are on is printed to the console) and simply set the start of the for-loop. After restarting the loop be sure to verify that the next downloaded page is the correct one, otherwise you will have to restart the process from step 1. While it may be tempting to reduce the Sys.sleep times to download faster (11 seconds delay per loop and 329 loops that's about 1 hour!), I found reducing the time cause errors as the pages were slow to load and thus ruining the process.

@@

# Proccessing Supplier
